\documentclass{article}

% - imports
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
% \usepackage[backend=biber]{biblatex-chicago}
% \addbibresource{bibliography.bib}
\usepackage{url}
\usepackage{parskip}
\usepackage{indentfirst}
\usepackage{parallel}

\title{\vspace*{-72pt} Title}
\author{Crystal Mandal}
\date{Last Edited \today}

\begin{document}

  \maketitle

  \section*{Question 1}
    I chose to focus on the poem ``Spring and Fall",
    by Gerard Manley Hopkins.
    \begin{enumerate}[label=(\alph*)]
      \item{The somber tone and the specific rhythmic notation
        (with the accents, as I understand they are used in English
        Poetry) are the primary elements that drew me to this
        poem. Also of relevance is the discourse of the interior
        of the child (if, I am, in fact, interpreting this in a
        reasonable way). I, for one, strongly believe in the
        agency of children, so a poem with a child subject
        experiencing and healing from grief is one that pains
        and intrigues me. Oh! poor child.}
      \item{I chose to listen to the songs ``Spring and Fall" and
        ``Margaret", by Ned Rorem and Alec Wilder, respectively.}
      \item{The rhythmic uncertainty that begins Rorem's setting is
        disorienting, but the harmonic content warms and familiarises
        us to the sound. Rorem's setting, as I understand, is
        quite idiomatic for his music. The use of suspended harmonies,
        displaced/disoriented rhythm, and the repeated melodic insistence
        on \(\hat{2}\) - that is, the second scale degree - lends itself
        to a particular sense of nostalgia and frigidity, as well as a
        very text-forward voice. Centering one note melodically
        provides a pitch foundation from which it is easier - for me,
        at least - to gleam the lyric content. In contrast, while I
        do quite love the musical content of the Wilder setting - as
        I love everything I hear of Alec Wilder - I have a difficult
        time discerning the lyric content of the voice. The choice
        of voice range - and thus, though I loathe to relate the two -
        an implicit characterization and \textit{gendering} of the
        narrator colour both settings differently, with Rorem and
        Wilder invoking a sort of Fatherly/Motherly duality. }
      \item{I think,
        as I listen to these settings while working, the Wilder setting
        is more immediately attractive, with its more straightforward
        melodic presentation, but the Rorem setting will remain in my
        heart. The subtlety of piano texture, rhythmic displacement,
        and \textit{very} controlled melodic contour are striking. }

    \end{enumerate}

  \clearpage{}

  \section*{Question 2}
    \begin{enumerate}[label=(\alph*)]
      \item{If this set is to adequately span Rorem's entire
        body of work, it's quite remarklable that both ``The Lordly
        Hudson" and ``Ferry me across the water" portray the river.
        Of the three, I'm quite struck by the contemporality of
        ``The Sick Wife" - the text is very modern, and points, to me,
        very clearly to the impact of postwar nuclearisation of
        the American Family - i.e. 1970s to 1990s. This focused
        temporality is, to me, unfamiliar in other writing we've
        studied. Musically, I would call none of the three songs
        quick. All of them are pensive and weighty - not dirges -
        without, as I hear, a performance of Grandeur. I am slowly
        but quite warmly growing accustomed to the harmonic language
        of Ned Rorem. }
      \item{It should be quite clear that my favourite of these
        three poems is ``The Sick Wife", by Jane Kenyon. My program note is as follows:

        Born in 1947, American poet Jane Kenyon died in 1995 after
        a year long struggle with leukemia. In 1996, her final
        collection of work, the posthumous \textit{Otherwise},
        contains a variety of poems, all from earlier years.
        As recounted by her husband, Donald Hall, in the Afterword,
        only two poems in the collection - and indeed, in Kenyon's
        entire work - were written after her diagnosis in January of 1994.
        Of the two, ``The Sick Wife" remains unfinished, Kenyon
        having passed while dictating the poem to a friend.
        Emblematic of Kenyon's contemporary positionality and her
        frequent fights with Depression, ``The Sick Wife",
        plainly and earnestly presents a haunting tapestry of disability,
        mundanity, and grief woven deeply into our American society.

      }
    \end{enumerate}
  \clearpage{}
  \section*{Question 3}

    These two songs are joyous as they are entirely indecipherable.
    While I can't in good conscience call either of their texts
    ``nonsense", neither are especially intelligble. The rapid
    stream of consciousness in ``English Usage" serves more to
    highlight the rhymes, rhythmic schemes, and vocal and linguistic
    playfulness, and the text of ``Love in the Dictionary" is, in fact, a
    strict Dictionary entry. Both pieces put voice front and center by
    forcing piano to a quiet, accompaniment role: neither piano part
    is especially interesting, but they do not have to be! Though I,
    as a pianist, would not especially enjoy learning these pieces, they
    are quite amusing to the listener.
    \begin{enumerate}[label=(\alph*)]
      \item{Earlier in the semester, we discussed a piece of French poetry - and
        an accompanying song - that had a similar effect. That song - unfortunately,
        the name escapes me - would be a perfect addition to a recital group, should
        you wish to create a ``nonsense" group.}
      \item{Unfortunately, I think these sorts of songs are a little too much of
        a joke for me to wish to programme them together. If I were putting together
        a recital group with these songs (separately) I might consider a holistic,
        abstract discourse on Love for ``Love in the Dictionary", and I might consider
        ``English Usage" as an ``interlude" piece. (I'm not sure if this is done in
        voice recitals, but in many instrumental recitals, I have been encouraged to put
        a shorter, ``lighter" piece between suites and major sonatas.)}
    \end{enumerate}

  \clearpage{}
  \section*{Question 4}
  In order, I would put ``The Lady who loved a Pig" first, ``Love in the Dictionary" second, and
  ``Serenader" last. I can't say I care much for the first piece, but it is joyful and quick,
  and easy listening. Love in the Dictionary is, to me, the most interesting of the three pieces,
  so it should be the focus of the recital group - in the middle. Finally, ``Serenader" is a
  beautiful ``ending" piece - slow in tempo, nostalgic, and sentimental. A perfect ending to a
  saccharine recital grouping.

  % \include{song-sheet-wanderer/song-sheet-wanderer.tex}
  % \include{song-sheet-contrabandista/song-sheet-contrabandista}
% \nocite{*}
% \printbibliography
\end{document}
