\documentclass{article}

% - imports
\usepackage{enumitem}
% \usepackage[backend=biber]{biblatex-chicago}
% \addbibresource{bibliography.bib}
\usepackage{url}
\usepackage{parskip}
\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{parallel}

\title{\vspace*{-72pt} Title}
\author{Crystal Mandal}
\date{Last Edited \today}

\begin{document}

  \maketitle

  \section*{Question 1}
    \begin{enumerate}[label=(\alph*)]
      \item{}\begin{enumerate}
          \item{Who is Chloris?}
          \item{To whom is Hahn writing all these love songs?}
          \item{I'd like some biographical information. Hahn isn't as
            well known as a composer as say, Franck, Fauré, or Ravel -
            other composers of French song. Where/when was he born? With
            whom did he study? What are some hallmarks of his style? What
            should I be listening for?}
      \end{enumerate}
      \item{The three are quite lovely self-contained love songs all by
        the same Composer. Putting them together as a Recital Set is,
        to me, a natural way to sample Hahn's musical styles. I don't
        have a particular inclination to which of \textit{Si mes vers}
        and \textit{Le printemps} should be first, but I do think that
        the end of \textit{À Chloris} is too intimate and lovely to
        not put at the end of the set.}
    \end{enumerate}

\clearpage{}

  \section*{Question 2}
  Topic Chosen: Why is ``Soupir" Challenging for a singer? Or is it?
  \subsection*{Response}
  First, I'm not sure I've heard this piece before, which is such a shame.
  This should be regarded among Ravel's most beautiful melodies alongside
  the G Major Piano Concerto and his String Quartet and Le Tombeau de
  Couperin. So many pieces of his don't even come close to the brilliance
  of instrumentation and melody and the balance of fantastic and grotesque
  he is so well known for that just \textit{shine} in this piece. And,
  just because of all of this minute detail, though I'm not convinced the
  physicality of this piece is too demanding - I'm not a well trained
  vocalist, so I might miss some things regarding technique - I'm
  quite convinced this must be \textit{impossible} to put together.
  I'm not sure, but does the tuning of the strings as harmonics
  require the vocalist to sing closer to a just intonation? If so,
  the piece would require a very well trained ear to even discern
  \textit{why} singing the ``right" notes still sounds ``off". The
  tempo ``Lent" at around 40bpm is just slow enough that an unaccustomed
  singer might find it difficult not to speed up. Of note, also, is the
  very strict rhythm over a very arhythmic accompaniment. The pitch
  and rhythm of the vocalist are almost entirely unsupported by the
  instrumentation. Overall, having to juggle the tuning, strict rhythms,
  and many little duet moments (with the flutes and violas), as well
  as the long phrasing (and, thus, I'd assume difficult breath control)
  make this, in my entirely uninformed opinion, quite challenging for
  a vocalist.

\clearpage{}

  \section*{Question 3}
    \subsection*{Recital Group}
      Total Length: 9:41
      \begin{enumerate}
        \item{Écoutez la chanson bien douce - Nadia Boulanger (6:03) }
        \item{Ach, die Augen sind es wieder - Nadia Boulanger (2:09) }
        \item{Chanson - Nadia Boulanger (1:29) }
      \end{enumerate}
      The obvious thread is that of the composer. Quite predictably,
      the Recital Group I've selected is comprised entirely of Boulanger
      songs. What strikes me about these pieces is the incredibly earnest
      and transparent nature of her music, as well as the absolute mastery
      of lyric and pianistic writing. The first song implores the audience
      "listen to the sweet song" that is to come. It's a love song, not
      for a particular person or character, but for the art of song itself.
      What follows is a short detour into a surprising second language for
      a French Composer. Another love song, though a little more explicit,
      \textit{Ach, die Augen sind es wieder} is musically and narratively
      compelling, with a touch of regret or other bittersweet
      sentimentality. I also firmly believe that it could be sung an
      octave higher to great success. The declaration of love by a higher,
      more conventional (or, as I like to think about it, more
      cisnormative or "cis-approachable") "woman's voice" to,
      in text, another woman queers the music and the space in which it
      is sung, inviting conversations about voice, position, and
      intentionality - and identity! - in musical performance.
      The last piece serves as a lighter "encore" gesture after two much
      more dramatic songs. \textit{Chanson} has some beautiful melodic
      writing and playfully quick rhythms with lots of interjections
      and "acting" involved.

  % \include{song-sheet-wanderer/song-sheet-wanderer.tex}
  % \include{song-sheet-contrabandista/song-sheet-contrabandista}
% \nocite{*}
% \printbibliography
\end{document}
