

\documentclass{article}

% - imports
\usepackage{enumitem}
\usepackage[backend=biber]{biblatex-chicago}
\addbibresource{bibliography.bib}
\usepackage{url}
\usepackage{parskip}
\usepackage{indentfirst}

\usepackage{parallel}

\title{\vspace*{-72pt} German 3}
\author{Crystal Mandal}
\date{Last Edited \today}

\begin{document}

  \maketitle

  \section*{Question 1}
  \begin{itemize}
    \item{I am very comfortable with recital planning as a pianist, so 
      many of the concepts are familiar to me. I am quite familiar with 
      the necessity of careful planning regarding the ``difficulty" (or, 
      in my opinion and in the case of a solo pianist, the physical 
      exhaustion) of performing the repertoire. In my last recital, I 
      put a great deal of thought into picking the repertoire to be 
      thematically and structurally cohesive.}
    \item{I did know about but have never really given any thought to the 
      number of songs sung in a recital. The text instructs us on a 
      ``standard" recital programme of five groups with four to six 
      songs each, or a total of almost \textit{thirty songs!} This is, 
      to me, an unthinkably long programme: even if I were to collect, 
      programme, and perform a collection of ``songs" and their 
      counterparts for piano, I couldn't imagine such a long programme. }
    \item{While I disagree with such explicit structuring or templating, 
      I do agree that it can be a great starting point. } 
    \item{I think I will have to do a great deal more of song literature 
      study to draft a recital programme I like.}
    \item{No questions for now, though I am, as evidenced by prior 
      performances, \textit{wholly} ignorant about and 
      usually unprepared for encores.}

  \end{itemize}

\section*{Question 2}

For this recital group, I have picked:
\begin{enumerate}
  \item{Im wunderschönen Monat Mai - R. Schumann Op. 48 No. 1 (~2 mins)}
  \item{Liebestreu - J. Brahms Op. 3 No. 1 (~2 mins)}
  \item{Die Mainacht - J. Brahms Op. 43 No. 2 (~3-4 mins)}
  \item{O Tod, wie bitter bist du - J. Brahms Op. 121 No 3. (~4-5 mins)}
  \item{Widmung - R. Schumann Op. 25 No. 1 (~2 mins)}
  % \item{Die Mainacht - Schubert}
\end{enumerate}
\textit{Total: approximately 13 to 15 minutes in length.}


Both my ignorance surrounding difficulty and style in vocal literature
and my personal insistence on gender-neutral voice casting in solo work
inform my amateurish assertion that these songs are all to be performed
by a single performer. I selected these pieces in particular for the
overall variety in character and texture, along with their general
reticence on love in various forms (and the recurring month of May).
Though I wanted to place \textit{Die Mainacht} and
\textit{Im wunderschönen Monat Mai} following one another, I was too
drawn to the lovely deceptive cadence outlined by the unresolved
$C\#^{7}$ chord at the end of the Schumann song directly into the
E-flat or ``D-sharp" tonality at the beginning of \textit{Liebestreu}.
Another fun relationship is the implicit, turbulent discourse on love
surrounding Robert Schumann, Johannes Brahms, and Clara Schumann. I
am yet undecided if the inclusion of a song by Clara Schumann would
undermine or distract from the dialogue between Robert Schumann and
Johannes Brahms (or if at all, in fact, this dialogue is meaningful or
interesting in any way).

\section*{Question 3}
For this question, I selected the Strauss pair for two very simple and 
insufficient reasons: 
\begin{enumerate}
  \item{I love Richard Strauss: Elektra is my favourite opera.}
  \item{I despise Mahler: he's not especially significant in piano 
    literature, and I keep mixing him up with Wagner - also unimportant 
    in piano literature - who has very good reasons to dislike, even if 
    the Liebestod from \textit{Tristan und Isolde} is among the most 
    beautiful things I've ever heard.}
\end{enumerate}

For the version with piano accompaniment: 
\begin{enumerate}
  \item{The clarity of the piano texture facilitates understanding of 
    Strauss' harmonic choices.}
  \item{The voice is never drowned out by the piano.}
  \item{A single instrumentalist can follow a vocalist in such an 
    intimate fashion that could never be replicated by an entire 
    ensemble. There's a brilliant recording of Christa Ludwig and 
    Leonard Bernstein arguing over tempo: in the end, Ludwig still 
    has to follow the conductor, but with a more intimate piano 
    accompaniment, a vocalist could instead lead the song in a 
    more natural, almost conversational tempo.}
\end{enumerate}

For the version with orchestral accompaniment: 
\begin{enumerate}
  \item{I believe Richard Strauss, unlike many others, is truly 
    capable of touching the sublime with his orchestration. Anything 
    of his with an orchestra involved is something substantial to 
    listen to and appreciate. }
  \item{Here, many inner voices and rhythms that are left out of the 
    piano part to facilitate playing and clarify the accompaniment are 
    given a proper treatment as beautiful additions to wind parts and 
    horn parts (especially, in my opinion, the addition of quicker 
    arpeggiated figures in the oboes). }
  \item{It is quite clear that Strauss is much more familiar with 
    an orchestral idiom than he is at the piano. The music is much 
    more recognizable to me as Strauss, and feels more ``comfortable", 
    compositionally.}
\end{enumerate}

\section*{Question 4}

As Roger Vignoles notes in his insightful commentary as found on Hyperion 
Records \autocite{hyperion-notes}, the piano part of these Mahler songs 
reflects Mahler's own familiarity with the orchestral idiom. Indeed, in 
this selection ``Hans und Grethe", the piano texture recalls the horns 
as depicted in the ritornello of Franz Liszt's fifth Paganini Etude 
or the first theme of Alkan's famed G Sharp Minor etude.

  % \include{song-sheet-wanderer/song-sheet-wanderer.tex}
  % \include{song-sheet-contrabandista/song-sheet-contrabandista}
\nocite{*}
\printbibliography
\end{document}
