\section*{The Apple Orchard - Lori Laitman}


You won’t remember it—the apple orchard\\
We wandered through one April afternoon,\\
Climbing the hill behind the empty farm.

A city boy, I’d never seen a grove\\
Burst in full flower or breathed the bittersweet\\
Perfume of blossoms mingled with the dust.

A quarter mile of trees in fragrant rows\\
Arching above us. We walked the aisle,\\
Alone in spring’s ephemeral cathedral.

We had the luck, if you can call it that,\\
Of having been in love but never lovers—\\
The bright flame burning, fed by pure desire.

Nothing consumed, such secrets brought to light!\\
There was a moment when I stood behind you,\\
Reached out to spin you toward me . . . but I stopped.

What more could I have wanted from that day?\\
Everything, of course. Perhaps that was the point—\\
To learn that what we will not grasp is lost.

\vspace{1.5in}

This composition is dedicated to the composer's father-in-law as a birthday
gift. Most birthday gifts are wrapped in decorative paper and maybe forgotten
in a few years This one will live forever in the hearts, minds, and souls of
everyone who ever encounters its kind, gentle beauty: unquestionably the best
80th birthday present ever given or received. The composer, Lori Laitman (b. 1955)
is still alive. It is unfortunately rare to have your
compositions programmed and performed, and rarer still to have your
music widely loved when your heart is still beating and your pen is
still writing. So much love surrounds this piece - in the gifting, in the writing,
in our listening - and it shows. The soft, dance-like figurations lead into
a rich, almost syrupy-smooth vocal line, with the most breathtakingly gorgeous
melody one can imagine : such is the musical language of Lori Laitman. It's a
surprise, then, that Laitman considers herself an ``Accidental" Vocal Composer.
In her own words, Laitman was drawn to the ``evocative story and exquisite language"
of the poem, especially the image of ``spring's ephemeral cathedral". The poem
is written by Dana Gioia (also alive, born in 1950), and was set his permission,
and is taken from his collection \textit{Pity the Beautiful}.
