\documentclass{article}

% - imports
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[backend=biber]{biblatex-chicago}
\addbibresource{bibliography.bib}
\usepackage{url}
\usepackage{parskip}
\usepackage{indentfirst}
\usepackage{parallel}

\title{\vspace*{-72pt} Title}
\author{Crystal Mandal}
\date{Last Edited \today}

\begin{document}

  \maketitle

  \section*{Biography}
  Rebecca Clarke was born in 1886, just outside of London.
  In her own memoir, Clarke recalls her childhood as alienating,
  having been born to and raised by her immigrant parents. Unfortunately,
  this isolation is a recurring theme in the Rebecca Clarke story, as
  she was among the first women to perform in a professional orchestra.
  Throughout her career, Clarke struggled with an embedded systemic misogyny,
  fraught with incidents doubting the authorship of her music - surely
  such beautiful music couldn't be written \textit{by a woman?}
  While primarily regarded by her peers for her instrumental and chamber music -
  particularly her Viola Sonata and Rhapsody for Cello and Piano, both having
  been cemented in standard repertoire - Rebecca Clarke Society president Liane
  Curtis remarks that ``it is in the genre of song that the full breadth of her
  musical style and development is revealed."\autocite{clarke-article}

  \section*{Typed Notes}
    \subsection*{Biography}
      \begin{itemize}
          \item{Dates: 1886 - 1979}\begin{itemize}
              \item{American Father, German Mother (Child of Immigrants)}
              \item{POST WWII in America, died in New York}
          \end{itemize}
          \item{Education}\begin{itemize}
              \item{Violin at Royal Academy of Music}
              \item{Composition with Charles Villies Stafford}\begin{itemize}
                  \item{Stafford was teacher of Vaugh Williams, Holst, Bridge}
                  \item{Clarke was his woman student}
              \end{itemize}
          \end{itemize}
          \item{Career}\begin{itemize}
              \item{one of the first women in a professional orchestra}
              \item{``dried up" after 1932}
              \item{music revived in 1976 after a radio interview\autocite{clarke-article}}
          \end{itemize}
      \end{itemize}

  \subsection*{Works Overview}
    \begin{itemize}
      \item{Viola Sonata (1919)}
      \item{``Shy One" (1912)}
      \item{Rhapsody for Cello and Piano (1923) }
      \item{``Seal Man" (1926)}
    \end{itemize}

  \subsection*{Style Notes}
    \begin{itemize}
      \item{Extended Harmonies - 9ths, 11ths!!}
      \item{Shifting Meters}
      \item{Chord Planing - Beginning of ``The Cradle", ``The Cherry Blossom Wand"}
      \item{Modality >> Tonal Harmony - Beginning of the Viola Sonata, ``Cherry Blossom Wand"}
      \item{Almost all of her poets are British}
    \end{itemize}

  \subsection*{Notes For/Against Trever Hold}
  Clarke's biggest song ``Seal Man", seems a bit too long and
  complicated to fit within Hold's ideas of simplicity and
  lyricism, but much of Clarke's music is quite idiomatic of
  the English Romantic Song Idiom as detailled by Trevor Hold.
  I found minimal melismatic gestures, subtle text painting,
  and plenty of 9ths (as well as ``crunchier" harmonies that
  Hold was less fanciful of). Clarke's song has less counterpoint
  than her instrumental music, but her contrupuntal understanding
  is nonetheless everpresent in her music, so I'm not sure her
  music keeps very strictly to the minimal counterpoint required
  by Hold.

  \subsection*{Accessibility}
  Clarke's music is not widely available on IMSLP (though some of her
  more popular songs are). You can find publication information on
  rebeccaclarke.org, which is quite helpful!


\clearpage

  % \include{song-sheet-wanderer/song-sheet-wanderer.tex}
  % \include{song-sheet-contrabandista/song-sheet-contrabandista}
\nocite{*}
\printbibliography
\end{document}
